Ground state energy of quantum dots using the coupled cluster method

### 2018-04-12 project_2/article/article.tex
Add start of section on CC energy

@@

    \subsection{The coupled cluster approximation}
        We approximate the true wavefunction, $\ket{\Psi}$, of the system by the
        coupled cluster wavefunction, $\ket{\Psi_{\text{CC}}}$, defined as
        \begin{align}
            \ket{\Psi_{\text{CC}}}
            &\equiv e^{T}\ket{\Phi_0}.
        \end{align}

>>>>

\newcommand{\kslat}{\ket{\Phi_0}}
\newcommand{\bslat}{\bra{\Phi_0}}

\newcommand{\kcc}{\ket{\Psi_{\text{CC}}}}
\newcommand{\bcc}{\bra{\Psi_{\text{CC}}}}

@@

    \subsection{The coupled cluster approximation}
        We approximate the true wavefunction, $\ket{\Psi}$, of the system by the
        coupled cluster wavefunction, $\ket{\Psi_{\text{CC}}}$, defined as
        \begin{align}
            \ket{\Psi_{\text{CC}}}
            &\equiv e^{T}\ket{\Phi_0}
            = \para{
                \sum_{i = 0}^n
                \frac{1}{n!}T^n
            }\ket{\Phi_0},
        \end{align}
        where the \emph{cluster operator}, $T$, is given by a sum of
        $p$-excitation operators
        \begin{align}
            T &= T_1 + T_2 + \dots \\
            &=
            \sum_{ia}t_i^a\acr{a}\ade{i}
            + \para{\frac{1}{2!}}^2\sum_{ijab}
            t_{ij}^{ab}\acr{a}\acr{b}\ade{i}\ade{j}
            + \dots.
        \end{align}
        We will be looking at the \emph{doubles} approximation, that is
        \begin{align}
            T = T_{\text{CCD}} \equiv T_2.
        \end{align}

        \subsubsection{Energy of the coupled cluster approximation}
            When we're going to compute the energy of a system using the coupled
            cluster approximation we would ideally want to find the expectation
            value of the energy using the coupled cluster wavefunction.
            \begin{align}
                E = \bcc H\kcc.
            \end{align}
            As it turns out, this is an uncomfortable way of finding the energy
            as $T \neq T^{\dagger}$. Instead we will define what we call the
            \emph{similarity transformed Hamiltonian}. We plug the coupled
            cluster wavefunction into the Schrödinger equation.
            \begin{align}
                H\kcc = E\kcc.
            \end{align}
            Next, we left multiply with the inverse of the cluster expansion,
            i.e.,
            \begin{align}
                e^{-T}H\kcc = e^{-T}E\kcc
                = E \kslat.
            \end{align}
            Projecting this equation on the reference state we get
            \begin{align}
                E = \bslat e^{-T}H\kcc
                = \bslat e^{-T}He^{T}\kslat,
            \end{align}
            where in the latter inner-product we have located the similarity
            transformed Hamiltonian defined by
            \begin{align}
                \bar{H} \equiv e^{-T}He^{T}.
                \label{eq:similarity_transformed_hamiltonian}
            \end{align}
